### 2018-12-10 writing/thesis/chapters/methods.tex
Add more stuff.

% Stuff for numerics
\newcommand{\domain}{\Omega}
\newcommand{\broken}{\domain}
\newcommand{\cell}[1][i]{C_{#1}}
\newcommand{\boundary}{\partial \domain}
\newcommand{\sbasis}[1]{\Phi_{#1}}
\newcommand{\stbasis}[1]{\Phi_{#1}}
\newcommand{\testfunction}[1]{\Phi_{#1}}
\newcommand{\normal}{\bm{n}}

@@

\newcommand{\dsol}[1][h]{\bm{u}_{#1}}
\newcommand{\stpredictor}[1][h]{\bm{q}_{#1}}
\sidetitle{Corrector}
First, we multiply the system \cref{eq:conservation-law} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
We arrive at the so called weak formulation of the \textsc{pde} 
\begin{equation}
  \label{eq:weak-pde}
\intdt{\intdcell{
\testfunction{k} \pdv{\Q}{t}
}}
+
\intdt{\intdcell{
    \testfunction{k} \left( \div{F(\Q, \gradQ} \right)
}}
=
\intdt{\intdcell{
    \testfunction{k} S(\Q, \bm{x}, t)
}}
\end{equation}
\todo{Include gradient everywhere!}
\todo{Double check the following description}
We now replace the solution $\bm{Q}$ with so called spacetime-predictor $\stpredictor (\bm{x},t)$ into the weak form and write it as a polynomial using the representation of \cref{eq:cell-approx}.
Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
\begin{align}
\begin{split}
\label{eq:corrector}
\left(
\intdcell{
  \testfunction{k} \sbasis{l}
}
\right)
(\bm{u^{n+1} - u^{n}})
&+
\left(\intdt{\intdcell{
      \testfunction{k} \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
}}\right)
-\\
\left(\intdt{\intdcell{
    \gradient{\testfunction{k}} \cdot  \flux(\stpredictor)
}}\right)
&=
\left(\intdt{\intdcell{
      \testfunction{k} \source(\stpredictor)
}}\right)
\end{split}
\end{align}
The first term motivates an orthogonal basis as this leads to a diagonal mass matrix.

@@

\sidetitle{Boundary extrapolation and stuff}
\todo{Explain that stpredictor and fluxes are saved and extrapolated to boundary.
This is important because we extrapolate the gradient as well!}
Extrapolate unknowns to boundary, convert from our basis to basis on faces.
Then Riemann solver
and so on

\sidetitle{Full Scheme}
Maybe write algorithm?

\todo{Actually write this section\ldots}

\sidetitle{Riemann solver \textit{\&} timestep}
As a Riemann solver we use a simple Rusanov-flux that is adapted for diffusive problems
\begin{equation}
  \label{eq:rusanov-flux}
  \Riemann(q_h^-, \nabla q_h^-; g_h^+, \nabla q_h^+) \cdot \bm{n} =
  \frac{1}{2} \left(
    F(q_h^+, \nabla q_h^+) +
    F(q_h^-, \nabla q_h^-)
  \right) -
  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-),
\end{equation}
with a penalty term
\begin{equation}
  \label{eq:parabolic-penalty}
  s_\text{max}  = \max \left(
\maxConvEigen[q_h^-], \, \maxConvEigen[q_h^+]
\right) +
2 \eta \max \left(
\maxViscEigen[q_h^-], \, \maxViscEigen[q_h^+]
\right)
\end{equation}
and
\begin{equation}
  \eta = \frac{2N+1}{h \sqrt{\frac{1}{2} \pi}}.
\end{equation}
In this equation, $N$ is the polynomial order and $h$ is the side-length of an element.
The penalty term depends on the maximal absolute eigenvalues $\lambda_c$ and $\lambda_v$ \todo{
Eigenvalues of jacobian (in normal direction), maximal eigenvalues.}.
Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
and viscous part $\maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$.

@@

The hyperbolic flux is given by
\begin{equation}
  \label{eq:hyper-flux}
  \hyperFlux(\Q) = \hyperFluxDef,
\end{equation}
which are the Euler equations coupled with an advection equation.
The viscous flux is
\begin{equation}
  \label{eq:visc-flux}
  \viscFlux(\Q, \gradQ) = \viscFluxDef.
\end{equation}

Complete \textsc{pde}:
\begin{equation}
 \begin{array}{l}
 \text{mass cons.} \\
 \text{momentum cons.} \\
 \text{energy cons.} \\
 \text{cont.\ gas} 
\end{array}
:
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  + 
  \divergence{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}
 =
  \underbrace{
  \begin{pmatrix}
    S_{\Qrho\phantom{\Qrho}}\\
    S_{\Qj}\\
    S_{\QE}\\
    S_{\QZ}
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}

where $\pressure$, $\stressT$ and $(\kappa \nabla T)$ denote the pressure, stress tensor and heat flux respectively.
Temperature is denoted by $T$.

We close the system with the equation of state of an ideal gas
\begin{equation}
  \label{eq:eos}
  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ \right).
\end{equation}
The term $q_0 \QZ$ corresponds to the chemical energy, where $q_0$ is the heat release.
The temperature $T$ relates to pressure and density by the ideal gas law
\begin{equation}
  \label{eq:temperature}
 \frac{\pressure}{\Qrho} = RT,
\end{equation}
where $R$ is the specific gas constant.

We further introduce the ratio of specific heats $\gamma$ and the heat fraction for constant volume $c_v$ and constant volume $c_r$.
These constants are all fluid dependent and relate to each other by
\begin{align}
  \label{eq:fluid-constants}
  \begin{split}
  c_v &= \frac{1}{\gamma - 1} R \\
  c_p &= \frac{\gamma}{\gamma - 1} R\\
  R &= c_p - c_v\\
  \gamma &= \frac{c_p}{c_v}.
  \end{split}
\end{align}
\todo{Cite sth!}
We can finally define the heat conduction coefficient $\kappa$
\begin{equation}
  \label{eq:heat-conduction-coeff}
  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R
\end{equation}
where Prandtl number $\text{Pr}$ again depends on the fluid.

@@

The viscous effects are modeled by the stress tensor
\begin{equation}
  \label{eq:stress-tensor}
  \stressT(Q, \nabla Q) = \left(\frac{2}{3} \mu \nabla \cdot \Qv \right) -
  \mu \left( \nabla (\Qv) + \nabla ( \Qv )^\intercal \right).
\end{equation}

Max eigenvalue of convective part $\maxConvEigen$,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
and viscous part $\maxViscEigen$, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
is
\begin{align}
  \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho}
                                       , \frac{\gamma \mu}{\Pr \Qrho} \right)
\end{align}
with speed of sound $c = \sqrt{\gamma R T }$

@@

We introduce parallel reduce.

Reduce mean/std by~\cite{chan1982updating}

Criterion with threshold.
Justify by Chebychev's inequality?
\todo{Cite this!}
This criterion can be justified by Chebychev's inequality, which states that
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2}
\end{equation}
for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$ probability $\mathbb{P}$.

>>>>

% Stuff for numerics
\newcommand{\domain}{\Omega}
\newcommand{\broken}{\domain}
\newcommand{\cell}[1][i]{C_{#1}}
\newcommand{\boundary}{\partial \domain}
\newcommand{\sbasis}[1]{\Phi_{#1}}
\newcommand{\stbasis}[1]{\Phi_{#1}}
\newcommand{\testfunction}[1]{\Phi_{#1}}
\newcommand{\normal}{\bm{n}}
\newcommand{\dsol}[1][h]{\bm{u}_{#1}}
\newcommand{\stpredictor}[1][h]{\bm{q}_{#1}}

@@

\begin{algorithm}[H]
  \begin{algorithmic}
    \Let{$\stpredictor$}{Initial guess}
    \Let{$F_h$}{$\flux(\Q, \gradQ)$}
    \Let{$\stpredictor$}{Solve \cref{eq:space-time-predictor} using $F_h, \Q, \gradQ$}
    \Let{$\left( \hat{F_h}, \hat{\Q}, \hat{\gradQ}, \hat{\stpredictor} \right)$}
        {Extrapolate to boundary using \cref{eq:boundary-extrapolation}}
    \Let{update}{Use \cref{eq:corrector} with boundary extrapolated values (fluxes of neighbors)}
  \end{algorithmic}
  \caption{The \textsc{ader-dg} algorithm for one cell.}
\end{algorithm}

\sidetitle{Corrector}
First, we multiply the system \cref{eq:conservation-law} by a test function $\testfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
We arrive at the so called weak formulation of the \textsc{pde} 
\begin{equation}
  \label{eq:weak-pde}
\intdt{\intdcell{
\testfunction{k} \pdv{\Q}{t}
}}
+
\intdt{\intdcell{
    \testfunction{k} \left( \div{F(\Q, \gradQ} \right)
}}
=
\intdt{\intdcell{
    \testfunction{k} S(\Q, \bm{x}, t)
}}
\end{equation}
\todo{Include gradient everywhere!}
\todo{Double check the following description}
We now replace the solution $\bm{Q}$ with so called spacetime-predictor $\stpredictor (\bm{x},t)$ into the weak form and write it as a polynomial using the representation of \cref{eq:cell-approx}.
Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
\begin{align}
\begin{split}
\label{eq:corrector}
\left(
\intdcell{
  \testfunction{k} \sbasis{l}
}
\right)
(\bm{u^{n+1} - u^{n}})
&+
\left(\intdt{\intdcell{
      \testfunction{k} \Riemann(\stpredictor^-, \stpredictor^+) \cdot \normal
}}\right)
-\\
\left(\intdt{\intdcell{
    \gradient{\testfunction{k}} \cdot  \flux(\stpredictor)
}}\right)
&=
\left(\intdt{\intdcell{
      \testfunction{k} \source(\stpredictor)
}}\right)
\end{split}
\end{align}
The first term motivates an orthogonal basis as this leads to a diagonal mass matrix.

@@

\sidetitle{Boundary extrapolation and stuff}
\todo{Explain that stpredictor and fluxes are saved and extrapolated to boundary.
This is important because we extrapolate the gradient as well!}
Extrapolate unknowns to boundary, convert from our basis to basis on faces and so on

\sidetitle{Riemann solver \textit{\&} timestep}
As a Riemann solver we use a simple Rusanov-flux that is adapted for diffusive problems
\begin{equation}
  \label{eq:rusanov-flux}
  \Riemann(q_h^-, \nabla q_h^-; g_h^+, \nabla q_h^+) \cdot \bm{n} =
  \frac{1}{2} \left(
    F(q_h^+, \nabla q_h^+) +
    F(q_h^-, \nabla q_h^-)
  \right) -
  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-),
\end{equation}
with a penalty term
\begin{equation}
  \label{eq:parabolic-penalty}
  s_\text{max}  = \max \left(
\maxConvEigen[q_h^-], \, \maxConvEigen[q_h^+]
\right) +
2 \eta \max \left(
\maxViscEigen[q_h^-], \, \maxViscEigen[q_h^+]
\right)
\end{equation}
and
\begin{equation}
  \eta = \frac{2N+1}{h \sqrt{\frac{1}{2} \pi}}.
\end{equation}
In this equation, $N$ is the polynomial order and $h$ is the side-length of an element.
The penalty term depends on the maximal absolute eigenvalues of both the convective and viscous part of the equations
\begin{align}
  \begin{split}
    \maxConvEigen &= \left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \normal,\\
    \maxViscEigen &= \left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \normal \right)\right) \cdot \normal,
  \end{split}
\end{align}
in direction of the normal vector $\normal$ to the cell face.

@@

The hyperbolic flux is given by
\begin{equation}
  \label{eq:hyper-flux}
  \hyperFlux(\Q) = \hyperFluxDef,
\end{equation}
which are the Euler equations coupled with an advection equation.
The viscous flux is
\begin{equation}
  \label{eq:visc-flux}
  \viscFlux(\Q, \gradQ) = \viscFluxDef.
\end{equation}
where $\pressure$, $\stressT$ and $(\kappa \nabla T)$ denote the pressure, stress tensor and heat flux respectively.
Temperature is denoted by $T$.

Putting everything together, our complete \textsc{pde} is a conservation law of the form of \cref{eq:conservation-law-gradient}
\begin{equation}
 \begin{array}{l}
 \text{mass cons.} \\
 \text{momentum cons.} \\
 \text{energy cons.} \\
 \text{cont.\ gas} 
\end{array}
:
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  + 
  \divergence{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}
 =
  \underbrace{
  \begin{pmatrix}
    S_{\Qrho\phantom{\Qrho}}\\
    S_{\Qj}\\
    S_{\QE}\\
    S_{\QZ}
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}

We close the system with the equation of state of an ideal reacting gas
\begin{equation}
  \label{eq:eos}
  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ \right).
\end{equation}
The term $q_0 \QZ$ corresponds to the chemical energy, where $q_0$ is the heat release.
The temperature $T$ relates to pressure and density by the ideal gas law
\begin{equation}
  \label{eq:temperature}
 \frac{\pressure}{\Qrho} = RT,
\end{equation}
where $R$ is the specific gas constant.

We further introduce the ratio of specific heats $\gamma$ and the heat fraction for constant volume $c_v$ and constant volume $c_r$.
These constants are all fluid dependent and relate to each other by
\begin{align}
  \label{eq:fluid-constants}
  \begin{split}
  c_v &= \frac{1}{\gamma - 1} R \\
  c_p &= \frac{\gamma}{\gamma - 1} R\\
  R &= c_p - c_v\\
  \gamma &= \frac{c_p}{c_v}.
  \end{split}
\end{align}
\todo{Cite sth!}
We can finally define the heat conduction coefficient $\kappa$
\begin{equation}
  \label{eq:heat-conduction-coeff}
  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R = \frac{\mu \gamma}{\Pr} c_v
\end{equation}
where Prandtl number $\Pr$ again depends on the fluid.

@@

The viscous effects are modeled by the stress tensor
\begin{equation}
  \label{eq:stress-tensor}
  \stressT(Q, \nabla Q) =
  \mu
  \left(
  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
  \right).
\end{equation}

The maximal eigenvalues for convective and viscous part are
\begin{align}
  \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho},
                        \frac{\gamma \mu}{\Pr \Qrho},
                        \diffCoeff \right)
\end{align}
with speed of sound $c = \sqrt{\gamma R T }$.

@@

\newcommand{\gobs}{\operatorname{G}}
\newcommand{\mean}{\mu}
\newcommand{\std}{\sigma}
\newcommand{\variance}{\std^2}
\newcommand{\gobsCount}{n}
We want to compute the mean and the variance over all grid cells by performing only pairwise merge operations.
This allows us to minimize communication over nodes and allows for a simple implementation.
The simplest way to compute this would be by using the textbook definitions of mean and variance of a random variable $X$
\newcommand{\expectation}{\mathbb{E}}
\begin{align}
  \begin{split}
    \mu [X] &= \expectation \left[ X \right]\\
    \variance [X] &= \expectation \left[ X^2 \right] - \expectation \left[ X \right]^2.
  \end{split}
\end{align}
The reduction for the variance is numerically unstable when the variance is orders of magnitudes smaller than the mean as this can lead to catastrophic cancellations.
We thus compute the mean and variance with the parallel algorithm of~\cite{chan1982updating}.
To do this, we need to store three variables per computation unit:
the mean, the variance and the number of processed elements.
We collect these items in the vector $\gobs = (\mean, \variance, \gobsCount)$
We can then merge two pairs of observed variables by \cref{alg:merge-variance}.

\begin{algorithm}[ht]
  \begin{algorithmic}
% TODO: Special cases 
\Function{reduce-variance}{$\gobs_0, \gobs_1$}
\If{$\gobsCount_0 = 0$}
  \State\Return{$\mean_1, \variance_1, \gobsCount_1$}
\EndIf\
\If{$\gobsCount_1 = 0$}
  \State\Return{$\mean_0, \variance_0, \gobsCount_0$}
\EndIf\
  \Let{$\Delta$}{$\mean_1 - \mean_0$}  
  \Let{$\gobsCount_\Sigma$}{$\gobsCount_0 + \gobsCount_1$}
  \Let{$m_a$}{$\variance_0 (\gobsCount_0 - 1)$}
  \Let{$m_b$}{$\variance_1 (\gobsCount_1 - 1)$}
  \Let{$m_\Sigma$}{$\nicefrac{m_a + m_b + (\Delta^2 \gobsCount_0 \gobsCount_1)}{\gobsCount_\Sigma}$}
  \Let{$\mean_\Sigma$}{$\mean_0  \gobsCount_0 + \mean_1 \gobsCount_1$}
  \State\Return{$
    \nicefrac{\mean_\Sigma}{\gobsCount_\Sigma},
    \nicefrac{m_\text{total}}{\gobsCount_\Sigma - 1},
    \gobsCount_\Sigma
    $}
\EndFunction\
  \end{algorithmic}
  \caption{\label{alg:merge-variance}
    Merging two sets of reduced mean and variance~\cite{chan1982updating}}
\end{algorithm}
We then use a threshold criterion
\todo{Cite Chebychev, add concrete form of threshold.}
This criterion can be justified by Chebychev's inequality, which states that
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2}
\end{equation}
for an arbitrary distribution with mean $\mu$ and standard deviation $\sigma$ probability $\mathbb{P}$.

### 2018-12-10 writing/thesis/chapters/results.tex
Add more stuff.

\chapter{Results}
\section{Convergence Test}
\section{Accurate CFD}
\section{Accurate Clouds}
\section{AMR Efficiency}
\section{Reactive Euler \textit{\&} Navier Stokes}

>>>>

\chapter{Results}\label{chap:results}
\section{Convergence Test}
\newcommand{\error}{\operatorname{Total-Error}}
Before computing the error we first need to define the $L_p$ norms for a $p > 0$ by
% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
\begin{equation}
  \label{eq:Lp-nrom}
  \Vert f(x) \Vert_p = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
\end{equation}
We are interested in the total error which we define as the norm of the difference between an analytical solution $f(\bm{x}, t)$ and our approximation $\hat{f}(\bm{x}, t)$.
The error at a time $t$ is thus defined as
\begin{equation}
  \label{eq:error}
  \error(t,p) = \Vert f(\bm{x}, t) - \hat{f}(\bm{x}, t) \Vert_p.
\end{equation}

We first observe that for our approximation space $\broken$ we can split up the error as a sum over all cells
\begin{equation}
  \label{eq:lp-norm-broken}
 %\Vert f(\bm{x}) \Vert = \sum_{\cell[] \in \broken} \Vert f_{\cell[]} (\bm{x}) \Vert_p,
  \error(t,p) = \sum_{\cell[] \in \broken} \error_{\cell[]}(t,p)
\end{equation}
where $\error_{\cell[]}$ is the error in the cell $\cell[]$.

\todo{Describe how to integrate the error for cells, and effect of volume}
% We are now ready to integrate the error for each cell.
% The output contains the position and conserved variables of each point.
% Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
% The quadrature weights are associated with the reference cuboid.
% We thus need to map our element to the reference element, before we can compute the integral.

% Let $V$ denote the volume (or area) of each cell.
% For example, in two dimensions $V = \Delta x \, \Delta y$.
% The final result is then
% \begin{equation}
%   \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
% \end{equation}
% where we used the mapping to the reference triangle (integration by substitution).

For the limiting case of $p \to \infty$ we use the maximum point-wise error.

\section{Accurate CFD}
\section{Accurate Clouds}
\section{AMR Efficiency}
\section{Reactive Euler \textit{\&} Navier Stokes}

### 2018-12-10 writing/thesis/chapters/scenarios.tex
Add more stuff.

\subsection{The first Stokes Problem}
\todo{Do I actually want to include this? Bit boring scenario}
\cite{dumbser2010arbitrary}
\subsection{Taylor-Green Vortex}
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) cos(y) \\
- \cos(x) sin(y) 
    \end{pmatrix} \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \frac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
  \end{split}
\end{align}
\todo{Constants!}
$C = 100/\gamma$ \cite{dumbser2016high}

@@

>>>>

% \subsection{The first Stokes Problem}
% \todo{Do I actually want to include this? Bit boring scenario}
% \cite{dumbser2010arbitrary}

\subsection{Taylor-Green Vortex}
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) cos(y) \\
- \cos(x) sin(y) 
    \end{pmatrix} \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \frac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C
  \end{split}
\end{align}
\todo{Constants!}
$C = 100/\gamma$ \cite{dumbser2016high}

@@

\subsection{Lid-Driven Cavity Flow}
The lid-driven cavity flow is a very simple testing scenario for the Navier-Stokes equations.
We use a constant pressure of (what exactly) and a constant density $(\Qrho = 1.0)$ for the entire domain.
The flow is then driven entirely by the boundary conditions.
They consist in four no-slip walls where the upper wall has a constant velocity $\Qv = (1.0, 0)$.
This scenario is surprisingly difficult for an \textsc{ader-dg} scheme as the boundary conditions lead to a discontinuity at the top left corner.
There, the velocity of the wall is piece-wise constant.
Therefore, this scenario is a good choice to test the stability of the finite volume limiter.

\subsection{ABC-Flow}
We use theArnold–Beltrami–Childress (\textsc{abc}) flow as a simple example of a three-dimensional scenario~\cite{tavelli2016staggered}.
This scenario has, unlike the three-dimensional version of the Taylor-Green vortex, at least for the incompressible case an analytical solution
\begin{align}
  \label{eq:abc-flow}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1\\
  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
  \begin{pmatrix}
    \sin(z) + \cos(y)\\
    \sin(x) + \cos(z)\\
    \sin(y) + \cos(x)
  \end{pmatrix} \\
  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
  + C
  \end{split}
\end{align}
Thus, we can simulate this without periodic boundary conditions.
\todo{Analytical solution!}
